### 2021-12-16 documentos/pce.tex
Mapas PCE no son canales cuánticos
Sobre el uso de "PCE maps"

\pce{} maps are defined as those quantum channels\R{A1} that \textit{nullify} Pauli strings. In the case of one qubit, they consist of maps nullifying the averages $r_\alpha:=\langle \sigma_\alpha \rangle=\tr \left( \rho \sigma_\alpha \right)$ with $\alpha=1,2,3$. The three components $r_\alpha$ form the well-known \textit{Bloch vector} $\vec r$, describing one qubit density matrices,

@@

As mentioned above, \pce{} maps nullify Pauli strings, thus, consider the linear operations acting in the generalized Bloch vector $\vec r_{\vec \alpha}$,
\begin{equation}
	\paulicomponents \mapsto \taus \paulicomponents.
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1,
\label{eq:definition:Pauli}
\end{equation}
with $\tau_{\vec \alpha}$ either $1$ or $0$.
Similar to the qubit case, not every operation with this form is a \cptp{} map. For the operation to be trace preserving, it is easy to prove that $\tau_{\vec 0}=1$. On the other hand, constructing and evaluating the conditions for complete positivity is involved and is the main problem addressed in this paper. Moreover, these operations are by definition diagonal in the $\left\{ 2^{-N/2}\sigma_{\vec
\alpha} \right\}$ basis.

@@

It is worth noticing that the set of \pce{} maps overlaps with the set of ``Pauli diagonal channels constant on axes'' defined in Ref.~\cite{nathanson2007pauli}, consisting of convex combinations of \textit{quantum-classical} channels. In particular, it can be shown that quantum-classical channels defined with the eigenbasis of some set of $2^N-1$ commuting Pauli observables~\cite{Lawrence2002}, is a \pce{} map with exactly $ 2^N $ components equal to $1$s in its diagonal.

@@

For the two qubits case, the operations illustrated in~\eref{eq:definition:Pauli} can be pictured using $4\times 4$ tables, showing the positions of the $0$s and $1$s of the diagonal using the Pauli string basis, see~\fref{fig:two:qubit:examples}. This way of representing \pce{} maps turned out to be very useful for their analysis throughout this work.

>>>>

\pce{} maps are defined as those quantum channels\janote{David, los mapas PCE no son necesariamentecanales cuánticos. Por esto, 
estás siendo incosistente en el uso de ``\pce{} maps'' en las líneas \lr{A1}, \lr{A2} y \lr{A3} del PDF. 
Especialmente, en la línea \lr{A1} seguro te estás refiriendo a todos los 
mapas, no sólo a los canales cuánticos} that \textit{nullify} Pauli strings. 
\janote{Por el comentario que hice antes propongo la siguiente reformulación:} 
\janote{
\pce{} maps are defined as positive trace-preserving (PTP) maps that 
\textit{nullify} Pauli strings.}
In the case of one qubit, they consist of maps nullifying the averages $r_\alpha:=\langle \sigma_\alpha \rangle=\tr \left( \rho \sigma_\alpha \right)$ with $\alpha=1,2,3$. The three components $r_\alpha$ form the well-known \textit{Bloch vector} $\vec r$, describing one qubit density matrices,

@@

As mentioned above, \pce{} maps\R{A1} nullify Pauli strings, thus, consider the linear operations acting in the generalized Bloch vector $\vec r_{\vec \alpha}$,
\begin{equation}
	\paulicomponents \mapsto \taus \paulicomponents.
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1,
\label{eq:definition:Pauli}
\end{equation}
with $\tau_{\vec \alpha}$ either $1$ or $0$.
Similar to the qubit case, not every operation with this form is a \cptp{} map. For the operation to be trace preserving, it is easy to prove that $\tau_{\vec 0}=1$. On the other hand, constructing and evaluating the conditions for complete positivity is involved and is the main problem addressed in this paper. Moreover, these operations are by definition diagonal in the $\left\{ 2^{-N/2}\sigma_{\vec
\alpha} \right\}$ basis.

@@

It is worth noticing that the set of \pce{} maps \R{A2} overlaps with the set of ``Pauli diagonal channels constant on axes'' defined in Ref.~\cite{nathanson2007pauli}, consisting of convex combinations of \textit{quantum-classical} channels. In particular, it can be shown that quantum-classical channels defined with the eigenbasis of some set of $2^N-1$ commuting Pauli observables~\cite{Lawrence2002}, is a \pce{} map with exactly $ 2^N $ components equal to $1$s in its diagonal.

@@

For the two qubits case, the operations illustrated in~\eref{eq:definition:Pauli} can be pictured using $4\times 4$ tables, showing the positions of the $0$s and $1$s of the diagonal using the Pauli string basis, see~\fref{fig:two:qubit:examples}. This way of representing \pce{} maps\R{A3} turned out to be very useful for their analysis throughout this work.
